### 2021-04-29 article/article.tex
Updated article

			Similarly, when \texttt{spinsim} is set to spin one mode, it can solve Schroedinger equations of the form

@@

			\begin{align*}
				J_x &= \frac{1}{\sqrt{2}}\begin{pmatrix}
					0 & 1 & 0 \\
					1 & 0 & 1 \\
					0 & 1 & 0
				\end{pmatrix},&
				J_y &= \frac{1}{\sqrt{2}}\begin{pmatrix}
					0 & -i &  0 \\
					i &  0 & -i \\
					0 &  i &  0
				\end{pmatrix},\\
				J_z &= \begin{pmatrix}
					1 & 0 &  0 \\
					0 & 0 &  0 \\
					0 & 0 & -1
				\end{pmatrix},&
				Q &= \frac{1}{3}\begin{pmatrix}
					1 &  0 & 0 \\
					0 & -2 & 0 \\
					0 &  0 & 1
				\end{pmatrix}.
			\end{align*}

			\(J_x, J_y, J_z\) are regular spin operators, and \(Q\) is a quadratic operator, proportional to \(Q_{zz}\) as defined by Hamley et al \cite{hamley_spin-nematic_2012}, and \(Q_0\) as defined by Di et al \cite{di_dipolequadrupole_2010}.

		\subsubsection*{Parallelisation}
			Given that \(\psi(t)\) is a unit vector, it is possible to write \(\psi(t)\) in terms of a unitary transformation \(U(t, t_0)\) of the state \(\psi(t_0)\), for any time \(t_0\). If the system is solved this way, using a geometric method, we can guarantee that \(\psi(t)\) will always be a unit vector, which is not true with solvers in general.

			\begin{align*}
				\psi(t) &= U(t, t_0)\psi(t_0)
			\end{align*}

>>>>

			Similarly, when \texttt{spinsim} is set to spin one mode, it can solve the Schroedinger equation of the form

@@

			\begin{align*}
				J_x &= \frac{1}{\sqrt{2}}\begin{pmatrix}
					0 & 1 & 0 \\
					1 & 0 & 1 \\
					0 & 1 & 0
				\end{pmatrix},&
				J_y &= \frac{1}{\sqrt{2}}\begin{pmatrix}
					0 & -i &  0 \\
					i &  0 & -i \\
					0 &  i &  0
				\end{pmatrix},\\
				J_z &= \begin{pmatrix}
					1 & 0 &  0 \\
					0 & 0 &  0 \\
					0 & 0 & -1
				\end{pmatrix},&
				\textrm{and }Q &= \frac{1}{3}\begin{pmatrix}
					1 &  0 & 0 \\
					0 & -2 & 0 \\
					0 &  0 & 1
				\end{pmatrix}.
			\end{align*}

			The matrices \(J_x, J_y, J_z\) are regular spin operators, and \(Q\) is a quadrupole operator. Note that \(Q\) is proportional to \(Q_{zz}\) as defined by Hamley et al \cite{hamley_spin-nematic_2012}, and \(Q_0\) as defined by Di et al \cite{di_dipolequadrupole_2010}.

		\subsubsection*{Parallelisation}
			Given that \(\psi(t)\) is a unit vector, it is possible to write \(\psi(t)\) in terms of a unitary transformation \(U(t, t_0)\) of the state \(\psi(t_0)\), for any time \(t_0\). In other words, for any \(t_0,t \in \mathbb{R}\), there is a unitary transformation \(U(t, t_0)\) such that

			\begin{align*}
				\psi(t) &= U(t, t_0)\psi(t_0).
			\end{align*}
